%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage{ctex,ragged2e}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}
\kaishu

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \href{https://youjilyu.netlify.app/}{\textbf{{\LARGE Youji Lyu 吕有吉}}} & Email: \href{mailto:}{lyjecon@nankai.edu.cn}\\
\end{tabular*}
\smallskip

%-----------Employment-----------------
\vspace{-5pt}
\section{Employment}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Nankai University}{Tianjin, China}
    {Junior Lecturer of Risk Management and Insurance}{July 2021 - Present}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\vspace{-5pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Peking University}{Bejing, China}
      {PhD in Risk Management and Insurance}{July 2016 - June 2021}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Thesis:} Pension Expectation Bias: Impact Factors and Policy Implications}}}
    \resumeSubheading
    {Nankai University}{Tianjin, China}
    {BA in Economics}{July 2012 - June 2016}
  \resumeSubHeadingListEnd

%-----------Research Interests-----------------	
\vspace{-5pt}
\section{Research Interests}
\resumeSubHeadingListStart
	\resumeSubItem{Social Security}{\hfill Policy Evaluation of Pension Reform, Long-Term Care Insurance Design}
	\resumeSubItem{Population Ageing}{\hfill Dynamic Health Transition Estimation, Old Age Support, Chronic Diseases Management}
	\resumeSubItem{Behavioral Economics}{\hfill Expectation Bias, Social Network, Learning from Experience, Loss Aversion}
\resumeSubHeadingListEnd

%-----------Teaching Courses-----------------	
\vspace{-5pt}
\section{Teaching Courses}
\resumeSubHeadingListStart
    \resumeSubheading
    {Property and Liability insurance}{Undergraduates}
    {Compulsory Course for RMI Majors}{September 2022 - Present}
    \resumeSubheading
    {Insurance Law}{Undergraduates}
    {Voluntary Course}{September 2022 - Present}
    \resumeSubheading
    {Practice of Life and Health Insurance}{Undergraduates}
    {Voluntary Course}{February 2022 - Present}
\resumeSubHeadingListEnd

%%-----------Experience-----------------
%\vspace{-5pt}
%\section{Experience}
%  \resumeSubHeadingListStart
%    \resumeSubheading{Google Summer of Code - Submitty}{Remote}
%    {Student Developer (Full-time)}{May 2019 - Sep 2019}
%    \resumeItemListStart
%        \resumeItem{Discussion Forum Upgrades}
%          {Refactor forum for performance to handle large databases.}
%          \resumeItem{REST API for Discussion Forum}
%          {Symphony \& Twig based Forum parts converted to API-first interface.}
%          \resumeItem{Ratchet PHP WebSocket}{Implemented a WebSocket for low-latency real time exchange of posts and thread updates.}
%      \resumeItemListEnd
%\vspace{-5pt}
%    \resumeSubheading
%		{DataCamp Inc.}{Remote}
%		{Instructor (Part-time, Contractual)}{Dec 2018 -  Present}
%		\resumeItemListStart
%        \resumeItem{Project Course - Find Movie Similarity from Plot Summaries}
%          {Created project based course using Unsupervised learning and natural language processing.}
%        \resumeItem{Tutorial - Introduction to Reinforcement Learning}
%          {Created tutorial for Q-learning RL algorithm and  concepts.}
%        \resumeItem{Impact}{Course has been taken by 250+ students so far with 4.65 average rating.}
%		\resumeItemListEnd
%\resumeSubHeadingListEnd
\justifying
%-----------Publications-----------------
\vspace{-5pt}
\section{Publications}
\begin{enumerate}
  \item \textbf{吕有吉}, 景鹏和郑伟 (2021).  \href{https://kns.cnki.net/kcms/detail/detail.aspx?dbcode=CJFD&dbname=CJFDLAST2021&filename=JRYJ202101004&uniplatform=NZKPT&v=Dy2OTtraPRwQBCNyQyyTfnk0pDvMj5hhMOrx1D6UguBzHuWxZzM4m7wqNcS1S9Cj}{人口老龄化、养老保险基金缺口弥补与经济增长}, \textbf{金融研究}, (01): 51–70.
  \item 郑伟和\textbf{吕有吉} (2021).  \href{https://kns.cnki.net/kcms/detail/detail.aspx?dbcode=CJFD&dbname=CJFDLAST2021&filename=SHKK202102016&uniplatform=NZKPT&v=XHHYwOpyyL2LmGNfm4OqWUAI7PPKseUGo8kLctKSGNXjKnSWsIeHpDh5bFVReUc7}{公共养老金与居民养老财富储备关系探析——基于文献述评的方法}, \textbf{社会科学辑刊}, (02): 148-159+209.
  \item 郑伟, 姚奕, 刘子宁和\textbf{吕有吉} (2020).  \href{https://kns.cnki.net/kcms/detail/detail.aspx?dbcode=CJFD&dbname=CJFDLAST2020&filename=BXYJ202010005&uniplatform=NZKPT&v=R1BvzEknGiQEYRr62O-g_1rC0GBkkaLXc5MIXtpWArutUkiN9S3x3l5M5n-8pXL5}{长期护理保险制度的评估框架及应用:基于三个案例的分析}, \textbf{保险研究}, (10): 65–78.
  \item 郑伟, 韩笑和\textbf{吕有吉} (2022).  \href{https://kns.cnki.net/kcms/detail/detail.aspx?dbcode=CJFD&dbname=CJFDLAST2022&filename=SHKK202203015&uniplatform=NZKPT&v=OLFhN3uqd1sfiFgZUvlGr5bQOAWDN9kS2W_dWwzcS1LAX-0VsD0fJJWxyM41i7g8}{中国人口慢性病的总体状况与群体差异}. \textbf{社会科学辑刊}, (03): 139-149+209.
  \item Wei Zheng, \textbf{Youji Lyu}, Ruo Jia, and Katja Hanewald (2021). \href{https://www.cambridge.org/core/journals/journal-of-pension-economics-and-finance/article/abs/impact-of-expected-pensions-on-consumption-evidence-from-china/C765559B9ED1E8D1B1118C21514C59C5#}{The Impact of Expected Pensions on Consumption: Evidence from China}, \emph{\textbf{Journal of Pension Economics and Finance}}, forthcoming.
  \item Qiang Fu, \textbf{Youji Lyu}, Yuanjie Zhang, and Zenan Wu (2022). \href{https://www.sciencedirect.com/science/article/abs/pii/S0899825622000240}{Expectation-Based Loss Aversion in Contests}. \textbf{\emph{Games and Economic Behavior}}, forthcoming.
  \item 景鹏, 王明璐和\textbf{吕有吉} (2022). 人口老龄化、再分配政策与经济增长——基于政治经济一般均衡分析, \textbf{财贸研究}, 接收待刊发.
\end{enumerate}

%-----------Publications-----------------
\vspace{-5pt}
\section{Working Papers}
\begin{enumerate}
  \item Minglu Wang, Peng Jing, and \textbf{Youji Lyu}. Child Support Policies, Fertility and Economic Growth, Submitted.
  \item Hua Chen, Zining Liu, \textbf{Youji Lyu}, and Xiaoyu Yang. Does Public Pension Program Matter for Marriage? Evidence from China, Submitted. (Presented at the 2022 APRIA Annual Conference)
  \item \textbf{Youji Lyu}, Zining Lyu, Wei Zheng, and Yi Yao. The Role of Peer Effects in Forming pension expectations：Existence, Mechanism, and Impact. (Presented at the 2022 APRIA Annual Conference and the 2022 ARIA Annual Conference with the title "Peer Effects in Pension Expectations")
  \item \textbf{Youji Lyu}, Zining Lyu, Wei Zheng, and Yi Yao. Long-Term Care Insurance Puzzle: Policy Design and Health Dynamic. (Presented at the 2019 APRIA Annual Conference with the title "Imputed Willingness to Pay for Long-Term Care Insurance in China")
  \item \textbf{吕有吉}, 景鹏和郑伟 , 公共养老保险改革与收入不平等演化.
  \item \textbf{吕有吉 }, 郑伟和谢志伟 , 老农保参保经历与养老金预期.
  \item 郑伟 , 谢志伟 , \textbf{吕有吉}和韩笑, 慢病“长治”的经济困境：来自CHARLS的证据.
  \item \textbf{Youji Lyu}, Wei Zheng, Yi Yao, and Liu Zining. Health Lost Due to Pension Expectation Bias. (Presented at the 2019 APRIA Annual Conference and the 2019 ARIA Annual Conference with the title "The Health Implication of Health Insurance and Pension on Middle-Aged and Elderly People: Evidence from China")
\end{enumerate}

%-----------Grants-----------------
\vspace{-5pt}
\section{Grants - Public Funding}
\begin{enumerate}
  \item 中国农村人口养老问题研究, 2022年09月01日至2023年09月01日, 南开大学人文社会科学基本科研业务费专项资金项目, 课题负责人.
  \item 延迟退休、养老保险降费与收入不平等演化, 2023年01月01日 至2025年12月31日, 国家自然科学基金青年科学基金项目（批准号：72204126）, 课题负责人.
  \item 参赛者异质性与竞赛设计, 2022年01月01日 至2025年12月31日, 国家自然科学基金青年科学面上项目（批准号：7217\\3002）, 参与.
\end{enumerate}

\vspace{-5pt}
\section{Grants - Private Funding}
\begin{enumerate}
  \item \href{https://www.swissre.com/institute/dam/jcr:b40ed819-5639-412f-b56b-c230e92464f5/healthy-ageing-in-china.pdf}{Healthy Ageing in China: Expanding Health Protection for the Middle-Age and Elderly}, Swiss Re Institute Risk Dialogue Series, January 2019 - October 2020, Principal Executor.
  \item The impact factors and economic consequences of chronic diseases in China, Swiss Re Institute Risk Dialogue Series, January 2021 - Present, Principal Executor.
  \item 世界人身保险产品创新历史, 2022年03月12日至今, 泰康 保险集团 股份有限公司委托课题, 主要参与人.
\end{enumerate}

%-----------Media Articles-----------------
\vspace{-5pt}
\section{Media Articles}
\begin{enumerate}
  \item 养老金制度改革中的运行效率问题, 中国保险报, 2018-11-23（004）.
  \item 离不开的网络，理得清的风险, 中国保险报, 2018-12-27（004）.
  \item 养老保险提升健康老龄化水平, 中国保险报, 2019-07-02（004）.
  \item 集成电路和软件产业发展风险浅谈, 中国银行保险报, 2020-09-04（004）.
\end{enumerate}

%-----------Requirements for Students-----------------
\vspace{-5pt}
\section{Requirements for Students}
\begin{enumerate}
  \item \emph{\textbf{Curious}} about the Economics Issues
  \item \textbf{\emph{Fanatical}} about the Academic Work
  \item Attaches Great Importance to \emph{\textbf{Time Management}}
\end{enumerate}

%-----------Awards-----------------
%\vspace{-5pt}
%\section{Honors and Awards}
%\begin{description}[font=$\bullet$]
%\item {北京市优秀毕业生 - 2021年}
%\vspace{-5pt}
%\item {北京大学优秀毕业生 - 2021年}
%\end{description}



\end{document} 